humanCdGF_predict_cfu

### 2016-10-12 code/HumanCdGF_predict_cfu.Rmd
colonization notes
update regression labels

ggplot(data = rf_prediction, aes(x=observed, y=predicted, color = cage_id)) + geom_point() + 
  labs(x= 'Observed CFU (log10)', y = 'Predicted CFU (log10)',
       title = "Random Forest Prediction of Colonized C Difficile CFU from Day 0 Community") + 
  theme_bw() + xlim(0,9) + ylim(0,9) + 
  annotate('text', x=0.15*(max(rf_prediction$observed)), 
           y=0.95*(max(rf_prediction$predicted)), 
           label=paste0('R^2 = ', round(tail(rf_n_features$rsq, 1), 2)))

@@

cage_color <- rainbow(length(unique(rf_prediction$cage_id)))
for (i in seq_along(importance_final)) {
  partial_otu <- 
    partialPlot(rf_n_features, top_colonized_df, names(importance_final)[i],
                xlab='', main=paste(tax_label[i]), 
                ylim = c(min(top_colonized_df$log_cfu_med),max(top_colonized_df$log_cfu_med)))
  for(m in seq_along(unique(rf_prediction$cage_id))){
    cage <- unique(rf_prediction$cage_id)[m]
    points(y = top_colonized_df[rf_prediction$cage_id %in% cage, 'log_cfu_med'],
         x = top_colonized_df[rf_prediction$cage_id %in% cage , names(importance_final)[i]], 
         pch = 21, bg = cage_color[m])
  }
}
```

@@

ggplot(data = rf_cr_prediction, aes(x=observed, y=predicted, color = cage_id)) + geom_point() + 
  labs(x= 'Observed', y = 'Predicted',
       title = "Random Forest Prediction of Relative Colonization level of C Difficile from Day 0 Community") + 
  theme_bw() + xlim(0,1) + ylim(0,1) + 
  annotate('text', x=0.15*(max(rf_cr_prediction$observed)), 
           y=0.95*(max(rf_cr_prediction$predicted)), 
           label=paste0('R^2 = ', round(tail(rf_col_rate_features$rsq, 1), 2)))

@@

>>>>

ggplot(data = rf_prediction, aes(x=observed, y=predicted, color = cage_id)) + geom_point() + 
  labs(x= 'Observed CFU (log10)', y = 'Predicted CFU (log10)',
       title = "Random Forest Prediction of Colonized C Difficile CFU from Day 0 Community") + 
  theme_bw() + xlim(0,9) + ylim(0,9) + 
  annotate('text', x=0.15*(max(rf_prediction$observed)), 
           y=0.95*(max(rf_prediction$predicted)), parse = T,
           label=paste0('R^2 == ', round(tail(rf_n_features$rsq, 1), 2))) + 
  theme(legend.position = 'none')

@@

cage_color <- rainbow(length(unique(rf_prediction$cage_id)))
for (i in seq_along(importance_final)) {
  partial_otu <- 
    partialPlot(rf_n_features, top_colonized_df, names(importance_final)[i],
                xlab='', main=paste(tax_label[i]), 
                ylim = c(min(top_colonized_df$log_cfu_med),max(top_colonized_df$log_cfu_med)))
  for(m in seq_along(unique(rf_prediction$cage_id))){
    cage <- unique(rf_prediction$cage_id)[m]
    points(y = top_colonized_df[rf_prediction$cage_id %in% cage, 'log_cfu_med'],
         x = top_colonized_df[rf_prediction$cage_id %in% cage , names(importance_final)[i]], 
         pch = 21, bg = cage_color[m])
  }
}

@@

ggplot(data = rf_cr_prediction, aes(x=observed, y=predicted, color = cage_id)) + geom_point() + 
  labs(x= 'Observed', y = 'Predicted',
       title = "Random Forest Prediction of Relative Day 1 Colonization Level of C. Difficile from Day 0 Community") + 
  theme_bw() + xlim(0,1) + ylim(0,1) + 
  annotate('text', x=0.15*(max(rf_cr_prediction$observed)), 
           y=0.95*(max(rf_cr_prediction$predicted)), parse = T,
           label=paste("R^2 == ", round(tail(rf_col_rate_features$rsq, 1), 2))) + 
  theme(legend.position = 'none')

@@

Does not predict colonization rate as well  
  - could be due to removed (cage/inocula-sensitive) otus  
  - improper measurement of colonization rate  
  - colonization rate not microbiome dependent, may be dependent on host factors of acute infection
